\section{Ground Station}\label{sec:gs}

The ground station is, generally, a terrestrial radio station designed for planetary and extraplanetary telecommunication with aircrafts and spacecrafts, respectively. For planetary telecommunications, the ground station is located on the surface of the Earth and they communicate with the aircrafts by sending and receiving radio waves in a specific band of the spectrum. When a ground station successfully transmits radio waves to an aircraft or vice versa, it establiches a telecommunication link.

In this case, the ground station is prepared to control the UAV using an antenna to communicate and a computer to analyse the received data and to send some commands to the aircraft. As was described in the previous section, in order to accomplish the desired task, it was taken as an example the eBee. The monitorization of the movement of this aircraft is done using the eMotion software that should be installed in the base station computer.

eMotion is software that enables the user to plan, simulate, monitor and control the movement of the UAV. In the plan part it is possible to import the background map and to draw a polygon that will correspond to the area that the user wants to cover. Then the user needs to define some parameters, like the ground resolution and the eMotion will automatically generate a full flight plan, calculating the eBee’s required altitude and displaying its projected trajectory. It is also possible to correct some parameters of the generated trajectory that were not taking into account in the previous case, allowing, for instance, a fly over an uneven terrain.

Before the flight, it is possible to simulate the trajectory of the UAV using the eMotion's simulator. The simulation helps the user to understand how the camera will work during the flight and how will be the movement of the UAV, without putting the aircraft at risk. After the simulation, while the vehicle is flying, eMotion provides a real-time information displaying all the flight parameters, the battery level and the image acquisition progress. During the flight, it is possible to control the UAV using a tool that is available in this software. Every mistake can be corrected which allows the reconfiguration of the vehicle's flight plan and the change of the landing point. Hence, this system allows a full control of the aircraft since the plan of the trajectory until the control during the flight.